Browsing the Web of Factual Claims

### 2008-09-18 papers/web_of_ideas/web_of_ideas.tex
Re-did the user study findings. Improved some figures.

\section{Interaction Techniques}

@@

\begin{figure}[tb]
	\includegraphics[width=8.5cm]{../screenshots/claimbrowse.png}
	\caption{The Claim Organizer contains two claim browsers}
	\label{fig:claimbrowser}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
	\caption{The Claim Browser Allows one to browse the argument graph}
	\label{claimbrowse_diagram}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_zoom.png}
	\caption{Close up of a list of supporting claims}
	\label{claimbrowse_zoom}
	\end{center}
\end{figure}

@@

Response was generally positive, with some participants being very keen to use the tool soon. One partipant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it becomes publically available. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

@@

Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version. None of these problems re-occured during the second study.

Most participants in the first study, and all participants in the second study were able to get competent with the tool. Participants in the second study were able to use Think Link compentently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.

\idea{first study confused between claims and topic}
\idea{felt disoreintated by the fact that the interface used for saving snippets was different from the interface used for browsing them}

ere able to get competent with the tool.

\subsubsection{Snippet Creation Strategies}

\idea{selecting the first paragraph}

\idea{selecting a table}

\idea{wanted to have the same snippet make several claims}

\subsubsection{Claim Creation Strategies}

\idea{not sure how specific a claim should be}

\idea{several wanted to be able to use the text they had selected as the claim, particularly when no relevant claims existed}

\idea{Need for topics - Ronnie Wood}

\subsubsection{Claim Connection Strategies}

\idea{confused when needed to make an intermediate claim}
\idea{wanted to say ``related'' and didn't realize this was what topics were for. When told them they agreed that this was what they wanted}
\idea{connecting same event at different times}

All the participants were able to create new snippets. Participants had little difficulty identifying interesting claims being made by web pages, selecting appropriate sections of text, and either picking existing claims that were appropriate, or writing appropriate new claims. Most ($9/12$) stated that they found it easy to create new snippets and associate them with claims.
In the initial interface snippets were only highlighted when the margin was open. This confused some participants ($5/12$) who were surprised to not see their snippets highlighted when they created them. In the final interface, we addressed this problem by always highlighting snippets.

In the initial interface the button to open the margin was on the toolbar, next to the ``new snippet'' button. This led some participants ($4/12$) to get confused about which they should use in each case. In the final interface, we addressed this problem by putting the margin button on the side of the page, with a chevron to indicate that it will pull out a margin (Figure~\ref{marginpull}).

\begin{figure}[ht]
	\includegraphics[width=8.5cm]{../screenshots/snippetdialog_sm.jpg}
	\caption{First Prototype Snippet Creation Dialog}
	\label{oldsnippetbox}
\end{figure}

@@

Most ($7/12$) users got confused between topics and claims at some point, either entering a topic as a claim, or entering a claim as a topic. We felt that this was partly because the snippet creation interface (Figure~\ref{oldsnippetbox}) gave the user little impression of how their snippet would appear in the claim browser. In the final interface we addressed this problem by giving the snippet creation interface the same core UI as the claim browser interface (Section~\ref{newsnippet}). We also decided to change our name for a factual claim from ``point'' to ``claim''.

While most ($10/12$) reused a topic that they had created or someone else had created, many ($6/12$) had a tendency to ignore the suggestion box and type new claims rather than looking for existing claims that might be a good match for their snippet. For the final interface, we tried to encourage users to reuse existing claims rather than writing new ones by making it easier to browse existing claims from the snippet creation window, and requiring users to click a \includegraphics[width=0.3cm]{../images/add.png} button in order to create a new claim (Section~\ref{newsnippet}).

Our initial interface for claim browsing (Figure~\ref{oldbrowser}) caused several ($5/12$) to remark that they felt they were confused about where they were in the claim graph. This interface had a separate page for each claim or topic, rather than animating between them, making it easy to lose track of ones position in the graph of points. Several ($2/12$) remarked that part of the problem was that it wasn't obvious that the various boxes on the page were information about the claim in large text. For the final interface we addressed this problem by using animation to maintain a sense of where things were when the focus changed, and by placing information about a point around that point rather than in separate boxes (Section~\ref{claimbrowser}).

All users had some difficulty connecting existing claims together. The first four participants were a different interface in which new connections were made by clicking on an ``add'' button, and then typing the name of the claim into an auto-complete box. Users found this approach difficult as it required them to remember the text of claims that they had seen recently. In light of this, after the first four participants we switched to a drag and drop interface (Figure~\ref{oldbrowser}).

The drag and drop interface worked better. Most ($7/8$) users were eventually able to use the new interface proficiently. However all users initially found the drag and drop interface confusing, and no users guessed that they could connect existing points using drag and drop. We identified this as an area needing improvement in the next interface revision.

@@

Many ($7/12$) participants also expressed a desire to organize claims into connected arguments during their session. Of these seven, we noticed that four would alternate between creating new snippets and organizing their claims in the claim browser (Section~\ref{claimbrowser}). With each new claim, users would create relationships between existing claims.

Many ($6/12$) participants marked one claim as supporting another claim when in fact they should have both been marked as supporting a shared claim that needed to be created. For the final interface we tried to address this problem by making the graph structure of claims easier to visualize and making it easier to create new claims (Section~\ref{claimbrowser}).

Two participants wanted to mark up a table as being a snippet and were unsure what claim they should say it made. In both cases, the table was a table of gold medals from the Beijing Olympics. We identified this as an area that we should investigate adding support for, since a table can provide evidence for the truth of many interesting claims.

One participant falsely connected claims that were actually referring to similar events that took place at different times rather than really being the same event. We identified the need for Think Link to provide more support for identifying the point in time that a claim or snippet is discussing.

Most ($9/12$) stated that they found the tool easy to use, and many ($5/12$) expressed an interest in using it during their normal browsing in its current state. When asked what they would want to use Think Link for, the most popular uses were helping them write a document ($5/12$), helping them form a personal opinion ($5/12$), or helping them argue a point to others ($5/12$). Many ($5/12$) were interested in seeing claims and snippets identified by their friends. Two said they were not interested in seeing what other people thought was interesting. Three users expressed an interest in using Think Link in ways that do not fit well with the current design, including gathering information about products they might buy, or finding cheap flights.

Due to the nature of the task, few ($3/12$) participants browsed pages that contained claims highlighted by other people, and so we were not able to evaluate how people reacted to seeing such highlights. This was made a priority of the second study.

\todo{mention people not being sure how broad a topic should be}
\todo{mention people creating claim in one topic and not being found in other related topics}

\section{Evaluation Study}

The purpose of the second study was to evaluate whether the interface changes we had made in reaction to the first study had made the tool usable.

We recruited 6 paid participants. Four were female and two were male. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the semester meant that five of the participants were students. Since the second group was different demographically to the first group, it is not possible to make a direct comparison between their behaviours. However we were still able to make interesting observations about how users used the new interface.

\subsection{Study Protocol}

In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it. We gave each user a brief introduction to the aims of the tool, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlights and tell them to explore the interface. The second task was to identify claims on a page that had not been marked up and connect them appropriately to existing claims.

Unlike the first study, we specified the pages that our users should look at. This was because we wanted to see how users would react to seeing pages in which core claims had been marked up as snippets, and wanted to be sure that new snippets people identified had related claims in our database.

Participants were shown an interface that is largely identical to that described in Section~\ref{interface}. All changes are described in the text below.

All the participants were very enthusiastic about the new interface. Most \howmany participants expressed a strong interest in being able to use the tool now. One user commented ``I can see myself getting quite addicted to this''.

When shown a page with highlighted text, all users noticed that text had been highlighted and all users were able to infer that red highlight meant that the point was contentious. All users worked out that they could get more information about a claim by clicking on it. Most \howmany users did not immediately notice the presence of the margin button or the fact that Think Link had a margin feature, suggesting that the icon may need to be animated or perhaps made bigger.

Several \howmany users were very enthusiastic about the ability to see when other users thought a claim on a page was contentious, and the ability to quickly navigate to contradictory arguments. One user commented ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.

The problems we had identified with the prototype interface seemed to have been fixed --- though, given the different demographics, we cannot state this conclusively. Everybody found it easy to tell what the ``open margin'' and ``new snippet'' buttons did. Nobody got confused between topics and claims.

Users seemed to enjoy the process of browsing through the graph of claims, seeing what supporting and opposing arguments had been identified, and what snippets had been found about topics.

Many ($4/6$) wanted to have a ``back'' button to help them navigate through the claim graph, but all users were comfortable navigating backwards once they noticed that the place they had come from was shown as a link at the top of the display.

Most users \howmany still seemed to find the process of creating connections between existing claims confusing, at least at first. Several \howmany users tried to create a connection to an existing point by clicking on the \includegraphics[width=0.3cm]{../images/add.png} button, rather than by dragging the existing point over. This prompted us to display a message in this case (Figure~\ref{newdragmessage}). Most \howmany users did not not immediately realize that they could use drag and drop. This prompted us to add a prominent message at the top of the claim browser encouraging users to use drag and drop to organize claims and points. All users were able to successfully organize points and claims with drag and drop once they had realized that this is what they were supposed to do.

Many users \howmany uncovered a bug in our new snippet window. They would navigate to an existing claim and then click the \includegraphics[width=0.3cm]{../images/add.png} button to create a new supporting or opposing claim. However they would then click ``Save'' before they had pressed return to create the new claim, with the result that their new snippet was attached to the selected claim rather than the new claim. This bug was easily fixed...

One user said they wanted to be able to mark a claim on a web page as being wrong without having to find other snippets that argued against it. In future work we plan to offer such a feature by allowing users to say whether they believe a claim is true.

\todo{quote collection}

>>>>

\section{Interaction Techniques}
\label{interface}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/claimbrowse.png}
	\caption{The Claim Organizer contains two claim browsers}
	\label{fig:claimbrowser}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
	\caption{The Claim Browser Allows one to browse the argument graph}
	\label{claimbrowse_diagram}
	\end{center}
\end{figure}
\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_zoom.png}
	\caption{Close up of a list of supporting claims}
	\label{claimbrowse_zoom}
	\end{center}
\end{figure}

@@

Response was generally positive, with many participants being very keen to use the tool soon. One partipant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it becomes publically available. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

@@

Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version. None of these problems re-occured during the second study. We discuss some of these changes in the sections below.

Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link compentently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. Particpants in the second study said they found the tool ``very intuitive''.

\subsubsection{Browsing the Argument Graph}

%In the first study, several participants reported that they felt ``disorientated'' when browsing through the idea graph.
%
%Several participants in the second study seemed to enjoy the action of browsing through ideas.

\subsubsection{Creating a Snippet}

Users would often encounter a snippet that could be interpreted as making several interesting claims, and were unsure about what to do in such circumstances. Sometimes users would deal with this by writing a compound claim like ``Global Warming will cause X and Y''. While users could mark up the same snippet as making multiple claims, users seemed to find this confusing, suggesting that we may want support in the snippet creation interface for picking several claims that a snippet is making.

One special case of this was that several users wanted to mark up a table as a snippet. A table can usually be considered to be making several interesting claims and users were often confused about what they should say the table cliams. Our current guidance is that one should mark up a table as making the most interesting claims that that table makes. In other cases, a user wanted to mark up an image as a snippet. While Think Link does not currently support this, it might make sense to allow this if an interesting claim can be inferred from the image.

Some users expressed an interest in marking up a snippet as a primary source rather than a claim. For example they might find the text of an important speech or an Olympic results table. Several expressed a desire to have a new class of object that was neither a topic nor a claim, but instead just ``an interesting object relavent to this topic''.

Many users would consistently mark the first paragraph of an article as a snippet. This paragraph would frequently summarise the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.

\subsubsection{Chosing a Claim for a Snippet}

\begin{figure}[t]
	\includegraphics[width=8.5cm]{../screenshots/oldsnipcreate_diagram.png}
	\caption{Initial Prototype Snippet Creation Dialog}
	\label{oldsnippetbox}
\end{figure}

@@

We found that participants using this initial interface felt disorientated by the fact that the interface for creating snippets was different to the interface used for visualizing them. Participants would often confuse claims and topics, either entering a claim in the topic box, or a topic in the claim box. Several participants expressed confusion about the difference between the two. Participants would also often create new points and topics when appropriate points and topics already existed in the claim graph, even when the suggestion list was drawing their attention to a topic or claim that would have been appropriate.

For the second study, we used the interface described in Section~\ref{newsnippet}, which uses the same claim browser interface used for exploring the claim graph. We found that users of this interface had no difficulty distinguishing between claims and topics and were much more likely to reuse existing claims and topics. We theorized that part of the reason for increased reuse was that, because users could see the claim graph they were creating, they felt more motivation to keep it ``tidy'' by reusing existing claims.

Several users expressed confusion about how specific the claim made by a snippet should be, or when they should pick an existing claim rather than create a new one. For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should a new claim be created that contains the extra information?

Several users also expressed an interest in being able to use the text of the snippet they selected as the text of its claim, particularly for short snippets. We intentionally made this a little difficult to do in an attempt to encourage users to find existing claims that are appropriate, however this may have been a mistake as it also increases the amount of effort required to create a snippet.

\subsubsection{Connecting Claims}

Many participants expressed a desire to organize claims into connected arguments during their session.

Some users incorrectly marked one claim as supporting another when in fact they should have both been marked as supporting a third claim that needed to be created, or where an intermediate claim was needed. For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing environmental problems''. Users realized that the claims were related, but did not immediately recognize that they needed to create new claims in order to structure the relationship correctly. It is possible that creating correct logical claim structures may just be too difficult for some people. We hope that, if Think Link was deployed more widely many of the intermediate claims that were needed would already have been created and this problem would be reduced.

Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. Similarly, many users expressed a desire to mark claims as being ``related'' without supporting or opposing each other. For example ``America did not sign the Kyoto Protocol'' {\it is related to} ``America was right to not sign the Kyoto Protocol''. Our current advice in such circumstances is to use topics to group claims that are related. For example these claims could all be in a topic called ``America and the Kyoto Protocol''. Participants seemed comfortable with the idea of relating claims in this way when we pointed it out to them, but most participants needed to be told that this was a strategy they could use.

Several users got confused by claims that referred to similar events at different points in time. For example, one participant in the first study marked a two claims as opposing each other when each was true at the time that it was written. This is a particular problem when talking about breaking news events, where what claims are true can change fast. If Think Link is to be effective for describing such events then it is likely that it will need to have better support for identifying the {\it time} at which a claim was asserted to be true.

@@
